Experiment 1 of 4

### 2016-09-25 experiments/e1/writeup/e1.Rmd
made graph smaller so that text is relatively larger

```{r rtplot, echo = FALSE}
dodge=.06
rtplot = ggplot(rtdataplot1, aes(y=logrtNormed, x=Gap, group=Vgn, fill=Vgn, shape=Vgn, ymin=logrtNormed-ci, ymax=logrtNormed+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.3, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=3, position=position_dodge(dodge)) +
  ggtitle("Response time") + 
  ylab("log RT") + 
  xlab("Gap Size") +
  scale_fill_grey(name=element_blank(), start=0, end=1) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() ) +
  theme(aspect.ratio=1) + xlab("")
```

```{r erplot, echo=FALSE}
dodge=.06
erplot = ggplot(erdataplot1, aes(y=errorNormed, x=Gap, group=Vgn, fill=Vgn, shape=Vgn, ymin=errorNormed-ci, ymax=errorNormed+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.3, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=3, position=position_dodge(dodge)) +
  ggtitle("Error rate") + 
  ylab("error rate") + 
  xlab("Gap Size") +
  scale_fill_grey(name=element_blank(), start=0,end=1)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() )+
  theme(aspect.ratio=1) + xlab("")
```

```{r plotRTandErrorRates, fig.width=10, fig.height=4, message=FALSE, echo=FALSE}
grid.arrange(rtplot, erplot, ncol=2)
```

>>>>

```{r rtplot, echo = FALSE}
dodge=.06
rtplot = ggplot(rtdataplot1, aes(y=logrtNormed, x=Gap, group=Vgn, fill=Vgn, shape=Vgn, ymin=logrtNormed-ci, ymax=logrtNormed+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.3, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=2, position=position_dodge(dodge)) +
  ggtitle("Response time") + 
  ylab("Respone time (log (ms))") + 
  xlab("Gap Size") +
  scale_fill_grey(name=element_blank(), start=0, end=1, guide=FALSE) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() ) +
  theme(aspect.ratio=1) + xlab("")
```

```{r erplot, echo=FALSE}
dodge=.06
erplot = ggplot(erdataplot1, aes(y=errorNormed, x=Gap, group=Vgn, fill=Vgn, shape=Vgn, ymin=errorNormed-ci, ymax=errorNormed+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.3, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=2, position=position_dodge(dodge)) +
  ggtitle("Error rate") + 
  ylab("Error rate (proportion of errors)") + 
  xlab("Gap Size") +
  scale_fill_grey(name=element_blank(), start=0, end=1)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() )+
  theme(aspect.ratio=1) + xlab("")
```

```{r plotRTandErrorRates, fig.width=7.5, fig.height=3, message=FALSE, echo=FALSE}
grid.arrange(rtplot, erplot, ncol=2)
```
